Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-02 tex/MesnardoBarba2019.tex
Properly reference Table 5 of the manuscript

Microsoft Azure offers the possibility of taking advantage of surplus capacity with ``low-priority'' virtual machines that are substantially cheaper than ``dedicated'' ones (\ref{tab:nc_series}).
For example, the low-priority \texttt{NC24r} instance costs $0.792$ USD per hour, $5$ times cheaper than its dedicated counterpart.
The reader should keep in mind that low-priority virtual machines may not be available for allocation or may be preempted at any time.
Thus, low-priority instances should be avoided for long-running MPI jobs in pools where inter-node communication is enabled.
We only used dedicated virtual machines to run our CFD simulations.
Moreover, our job tasks used a shared filesystem (GlusterFS on compute nodes) for I/O operations and Batch Shipyard would fail to create the pool if low-priority nodes were requested.

>>>>

Microsoft Azure offers the possibility of taking advantage of surplus capacity with ``low-priority'' virtual machines that are substantially cheaper than ``dedicated'' ones (see Table \ref{tab:nc_series} for pricing options on the NC series with Linux-based virtual machines).
For example, the low-priority \texttt{NC24r} instance costs $0.792$ USD per hour, $5$ times cheaper than its dedicated counterpart.
The reader should keep in mind that low-priority virtual machines may not be available for allocation or may be preempted at any time.
Thus, low-priority instances should be avoided for long-running MPI jobs in pools where inter-node communication is enabled.
We only used dedicated virtual machines to run our CFD simulations.
Moreover, our job tasks used a shared filesystem (GlusterFS on compute nodes) for I/O operations and Batch Shipyard would fail to create the pool if low-priority nodes were requested.
